\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-03-15 presentations/cambridge-18-03-2019/illu-preamble.tex
[Presentation] First commit, Cambridge '19 presentation
[Presentation] Update Cambridge '19 presentation

@@

\newcommand{\capbrace}[3][sp1]{
  \draw [decorate,decoration={brace,amplitude=8pt,mirror,raise=3pt},yshift=0pt]
  #2 -- #3 node[draw=black] (#1) [black,midway,xshift=0.8cm] {};

}

>>>>

\newcommand{\regfile}{
      \draw (17.5,5.5) node {register file};
    \begin{scope}
      \clip (16.9,1.1) rectangle (18.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (17,\x) rectangle (18,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \coordinate (r1) at (17.5,4.5) {};
    \node[anchor=west] at (18.1,4.5) {$r_{\mathit{stk}}$};
    \coordinate (r2) at (17.5,3.5) {};
    \node[anchor=west] at (18.1,3.5) {$r_2$};
    \coordinate (r3) at (17.5,2.5) {};
    \node[anchor=west] at (18.1,2.5) {$r_3$};
}

@@

\newcommand{\capbrace}[3][sp1]{
  \draw [decorate,decoration={brace,amplitude=8pt,mirror,raise=4pt},yshift=0pt]
  #2 -- #3 node[draw=black] (#1) [black,midway,xshift=0.8cm] {};
}
